A word-sense representation for documents based on information value and word sense disambiguation

### 2014-04-01 paper/refactor.tex
Some aesthetical changes.
Rewrite some formulas.

where $f_w$ is the frequency of appearance of $w$ in $T$. This value captures, in some way, whether a word
has a distribution in text that is not exactly uniform; an order of the word in the text that brings some sense to it. 
Ordering the words by their information value results in a list of the text's most representative words. In the context of our research, we call the first $n$ words of a text -with $n$ fixed-, ordered by it's information value, the \textit{top words} of the document.

\begin{equation}
  top\_words_{n}(T) = \{w | max(IV_T(w))\}
\end{equation}

@@

Given a document $T$ and an arbitrary integer $n$, the \textit{top senses} are defined as follow:
\begin{equation}
  top\_senses_{n}(T) = \{s | w \in top\_words_{n}(T) \wedge  s = wsd_T(w)\}
\end{equation}

@@

@@

\appendix[All tables]
% \input{top_senses_the_state_and_revolution}
% \input{top_senses_lenin_imperialism_the_highest_stage_of_capitalism}
% \input{top_senses_lenin_materialism_and_empirio-criticism}
% \input{top_senses_lenin_the_agrarian_programme_of_social-democracy_in_the_first_russian_revolution_1905-1907}
% \input{top_senses_lenin_what_is_to_be_done?}

>>>>

where $f_w$ is the frequency of appearance of $w$ in $T$. This value captures, in some way, whether a word
has a distribution in text that is not exactly uniform; an order of the word in the text that brings some sense to it.

Ordering the words by their information value results in a list of the text's most representative words. In the context of our research, we call the first $n$ words of a text -with $n$ fixed-, ordered by it's information value, the \textit{top words} of the document.

That's it, if we have all the words sorted as $w_1, w_2, \ldots , w_M$ such that $ i \leq j \Rightarrow IV_{T}(w_i) >= IV_{T}(w_j)$, then, the $n$ top words are $w_1, w_2, \ldots w_n$

@@

Given $w_1, \ldots, w_M$, words of $T$ sorted by information value, and suppose that $w_{i_1}, w_{i_2}, \ldots, w_{i_n}$ are the $n$ first words  such that disambiguation for each $w_{i_j}$ is feasible. Then, the top senses for $T$ are
\begin{equation}
  WSD(w_1), WSD(w_2), \ldots, WSD(w_n)
\end{equation}

@@

\newpage

@@

\appendix[All tables]
